---
output:
  pdf_document: default
  html_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```{r}
View(Shoes...Sheet)
Shoes_Male <- subset(Shoes...Sheet, Gender == "M")
Shoes_Male
Shoes_Female <- subset(Shoes...Sheet, Gender == "F")
Shoes_Female
Mean_ShoeSize <- mean(Shoes...Sheet$ShoeSize)
Mean_Height <- mean(Shoes...Sheet$Height)
Mean_Shoes <- data.frame(Mean_ShoeSize, Mean_Height)
Mean_Shoes
months_vector <- c("March", "April", "January", "November", "January",
 "September", "October", "September", "November", "August",
 "January", "November", "November", "February", "May", "August",
 "July", "December", "August", "August", "September", "November", "February", 
 "April")
factor_months_vector <- factor(months_vector)
factor_months_vector
summary_months_vector <- summary(months_vector, factor_months_vector)
summary_months_vector
factor_data <- data.frame(
  Direction = c("East", "West", "North"),
  Frequency = c(1, 4, 3)
)
factor_data
new_order_data <- factor(factor_data,levels = c("East","West","North"))
print(new_order_data)
library(readr)
import_march <- read_csv("worksheet#4/import_march.csv")
View(import_march)
import_march <- read.table(import_march.csv)
import_march